---
title: "Network Psychometric Analysis of ELLIPSE Metrics"
subtitle: "Where Does Word Predictability Fit in L2 Writing Proficiency Structure?"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    self-contained: true
execute:
  warning: false
  message: false
---

# Overview

This analysis complements the CFA approach by using a data-driven
Gaussian Graphical Model (GGM) to empirically discover how word predictability relates
to other linguistic features — without imposing a factor structure.

**Key question:** Does word predictability (`mean_loss`) cluster with
phraseological, lexical, or other features — or does it form its own community?

# Section 1 — Setup & Data Preparation

```{r}
#| label: setup
library(tidyverse)
library(psych)
library(corrplot)
library(qgraph)
library(bootnet)
library(networktools)
library(igraph)
library(EGAnet)
library(lavaan)
```

```{r}
#| label: load-data
df_raw <- read.csv("../../data/ellipse_metrics.csv")

cat("Raw data:", nrow(df_raw), "rows x", ncol(df_raw), "columns\n")
```

```{r}
#| label: select-features

# Select the 16 feature variables
feature_vars <- c(
  # Lexical (4)
  "mtld", "lexical_density", "log_mean_token_freq", "mean_word_length",
  # Syntactic (4 planned, but clauses_per_tunit is constant)
  "words_per_sentence", "clauses_per_tunit", "mod_per_nom", "mean_dep_distance",
  # Phraseological (3)
  "amod_mi", "dobj_mi", "advmod_mi",
  # Cohesion (3)
  "content_word_overlap", "connective_density", "sentence_similarity",
  # Predictability (1)
  "mean_loss"
)

df_features <- df_raw[, feature_vars]

# Check clauses_per_tunit variance
cat("clauses_per_tunit — unique values:", length(unique(df_features$clauses_per_tunit)),
    "| sd:", sd(df_features$clauses_per_tunit, na.rm = TRUE), "\n")

# Drop clauses_per_tunit — zero variance (all values = 1)
df_features$clauses_per_tunit <- NULL
cat("Dropped clauses_per_tunit (constant). Remaining:", ncol(df_features), "variables\n")
```

```{r}
#| label: check-collinearity

# mean_entropy removed due to near-perfect correlation with mean_loss (r = 0.97)
# which created a trivial island in the network
cat("Note: mean_entropy excluded (r = 0.97 with mean_loss). Using mean_loss only.\n")
```

```{r}
#| label: missing-data

# Report missingness
missing_counts <- colSums(is.na(df_features))
cat("Missing values per variable:\n")
print(missing_counts[missing_counts > 0])
cat("\nTotal rows before listwise deletion:", nrow(df_features), "\n")

# Listwise deletion
df_complete <- df_features %>% drop_na()
cat("Total rows after listwise deletion:", nrow(df_complete),
    "(dropped", nrow(df_features) - nrow(df_complete), "rows)\n")
```

```{r}
#| label: winsorize

# Winsorize at 1st/99th percentiles
winsorize <- function(x, probs = c(0.01, 0.99)) {
  q <- quantile(x, probs = probs, na.rm = TRUE)
  x[x < q[1]] <- q[1]
  x[x > q[2]] <- q[2]
  x
}

# Show pre-winsorization extremes for key variables
cat("Pre-winsorization extremes:\n")
cat("  words_per_sentence: max =", max(df_complete$words_per_sentence), "\n")
cat("  connective_density: max =", max(df_complete$connective_density), "\n")

df_win <- df_complete %>%
  mutate(across(everything(), winsorize))

cat("\nPost-winsorization extremes:\n")
cat("  words_per_sentence: max =", max(df_win$words_per_sentence), "\n")
cat("  connective_density: max =", max(df_win$connective_density), "\n")
```

```{r}
#| label: define-groups

# Theoretical groupings for coloring (after dropping clauses_per_tunit)
groups <- list(
  Lexical       = c("mtld", "lexical_density", "log_mean_token_freq", "mean_word_length"),
  Syntactic     = c("words_per_sentence", "mod_per_nom", "mean_dep_distance"),
  Phraseological = c("amod_mi", "dobj_mi", "advmod_mi"),
  Cohesion      = c("content_word_overlap", "connective_density", "sentence_similarity"),
  Predictability = c("mean_loss")
)

# Short labels for plotting
short_labels <- c(
  mtld = "MTLD",
  lexical_density = "LexDen",
  log_mean_token_freq = "TokFreq",
  mean_word_length = "WordLen",
  words_per_sentence = "WPS",
  mod_per_nom = "ModNom",
  mean_dep_distance = "DepDist",
  amod_mi = "AmodMI",
  dobj_mi = "DobjMI",
  advmod_mi = "AdvMI",
  content_word_overlap = "CWO",
  connective_density = "ConnDen",
  sentence_similarity = "SentSim",
  mean_loss = "Loss"
)

# Color scheme
group_colors <- c(
  Lexical = "#E41A1C",        # red
  Syntactic = "#377EB8",      # blue
  Phraseological = "#4DAF4A", # green
  Cohesion = "#FF7F00",       # orange
  Predictability = "#984EA3"  # purple
)

# Map each variable to its group color
node_colors <- character(ncol(df_win))
names(node_colors) <- names(df_win)
for (g in names(groups)) {
  node_colors[groups[[g]]] <- group_colors[g]
}
```


# Section 2 — Descriptive Statistics & Correlation Matrix

```{r}
#| label: descriptive-stats
#| tbl-cap: "Descriptive statistics for all network variables"

desc_stats <- describe(df_win)
print(desc_stats[, c("n", "mean", "sd", "min", "max", "skew", "kurtosis")], digits = 3)
```

```{r}
#| label: correlation-heatmap
#| fig-cap: "Pearson correlation matrix of all network variables"
#| fig-width: 10
#| fig-height: 9

cor_mat <- cor(df_win, use = "pairwise.complete.obs")

# Use short labels for readability
colnames(cor_mat) <- short_labels[colnames(cor_mat)]
rownames(cor_mat) <- short_labels[rownames(cor_mat)]

corrplot(cor_mat, method = "color", type = "lower",
         tl.col = "black", tl.cex = 0.9,
         addCoef.col = "black", number.cex = 0.6,
         col = colorRampPalette(c("#2166AC", "white", "#B2182B"))(200),
         diag = FALSE)
```

```{r}
#| label: normality-check
#| fig-cap: "Distribution of all network variables"
#| fig-width: 12
#| fig-height: 10

df_win %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  mutate(variable = short_labels[variable]) %>%
  ggplot(aes(x = value)) +
  geom_histogram(bins = 40, fill = "steelblue", color = "white", linewidth = 0.2) +
  facet_wrap(~ variable, scales = "free", ncol = 4) +
  theme_minimal(base_size = 11) +
  labs(x = NULL, y = "Count")
```


# Section 3 — Network Estimation (EBICglasso)

```{r}
#| label: estimate-network

# Estimate Gaussian Graphical Model using EBICglasso
network <- estimateNetwork(df_win, default = "EBICglasso", tuning = 0.5)

cat("Network estimated with", ncol(network$graph), "nodes\n")
cat("Non-zero edges:", sum(network$graph[upper.tri(network$graph)] != 0),
    "out of", sum(upper.tri(network$graph)), "possible\n")
cat("Sparsity:", round(1 - mean(network$graph[upper.tri(network$graph)] != 0), 3), "\n")
```

```{r}
#| label: adjacency-matrix
#| tbl-cap: "Weighted adjacency matrix (partial correlations)"

adj_mat <- round(network$graph, 3)
colnames(adj_mat) <- short_labels[colnames(adj_mat)]
rownames(adj_mat) <- short_labels[rownames(adj_mat)]
print(adj_mat)
```


# Section 4 — Network Visualization

```{r}
#| label: network-spring
#| fig-cap: "GGM network (spring layout, Fruchterman-Reingold)"
#| fig-width: 10
#| fig-height: 10

# Assign short labels for the plot
net_labels <- short_labels[colnames(network$graph)]

spring_layout <- qgraph(network$graph,
       layout = "spring",
       labels = net_labels,
       groups = groups,
       color = group_colors,
       legend = TRUE,
       legend.cex = 0.45,
       borders = TRUE,
       border.width = 1.5,
       vsize = 8,
       esize = 8,
       edge.color = NULL,
       posCol = "#2166AC",
       negCol = "#B2182B",
       title = "ELLIPSE Linguistic Features — GGM Network",
       title.cex = 1.2)
```

```{r}
#| label: save-spring-plot
#| include: false

pdf("../../fig/network_spring.pdf", width = 10, height = 10)
qgraph(network$graph,
       layout = "spring",
       labels = net_labels,
       groups = groups,
       color = group_colors,
       legend = TRUE,
       legend.cex = 0.45,
       borders = TRUE,
       border.width = 1.5,
       vsize = 8,
       esize = 8,
       posCol = "#2166AC",
       negCol = "#B2182B",
       title = "ELLIPSE Linguistic Features — GGM Network")
dev.off()
cat("Saved to fig/network_spring.pdf\n")
```

```{r}
#| label: network-circle
#| fig-cap: "GGM network (circle layout)"
#| fig-width: 10
#| fig-height: 10

qgraph(network$graph,
       layout = "circle",
       labels = net_labels,
       groups = groups,
       color = group_colors,
       legend = TRUE,
       legend.cex = 0.45,
       borders = TRUE,
       border.width = 1.5,
       vsize = 8,
       esize = 8,
       posCol = "#2166AC",
       negCol = "#B2182B",
       title = "ELLIPSE Linguistic Features — GGM Network (Circle)")
```


# Section 5 — Centrality Analysis

```{r}
#| label: centrality-plot
#| fig-cap: "Centrality indices for all nodes"
#| fig-width: 10
#| fig-height: 8

centralityPlot(network$graph, labels = net_labels,
               include = c("Strength", "Betweenness", "Closeness", "ExpectedInfluence"),
               orderBy = "Strength")
```

```{r}
#| label: centrality-table
#| tbl-cap: "Centrality values for all nodes"

cent <- centrality_auto(network$graph)$node.centrality
cent$Variable <- short_labels[rownames(cent)]
cent <- cent %>% select(Variable, everything())
print(cent %>% arrange(desc(Strength)), digits = 3)
```

```{r}
#| label: predictability-edges
#| tbl-cap: "Edge weights involving predictability nodes"

# Extract edges for mean_loss
adj <- network$graph
loss_edges <- adj["mean_loss", ]

pred_edges <- data.frame(
  Partner = short_labels[names(loss_edges)],
  Loss_edge = round(loss_edges, 3)
) %>%
  filter(Partner != "Loss") %>%
  arrange(desc(abs(Loss_edge)))

cat("Strongest connections of mean_loss:\n")
print(pred_edges)
```


# Section 6 — Community Detection (EGA)

```{r}
#| label: ega
#| fig-cap: "Exploratory Graph Analysis — community detection"
#| fig-width: 10
#| fig-height: 10

ega_result <- EGA(df_win, model = "glasso",
                  algorithm = "walktrap",
                  plot.EGA = TRUE)

cat("\nNumber of communities detected:", ega_result$n.dim, "\n")
cat("\nCommunity assignments:\n")

# Show assignments with short labels
assignments <- data.frame(
  Variable = short_labels[names(ega_result$wc)],
  Full_name = names(ega_result$wc),
  Community = ega_result$wc
)
print(assignments %>% arrange(Community))
```

```{r}
#| label: ega-predictability

# Highlight where predictability ended up
cat("Predictability node assignment:\n")
cat("  mean_loss -> Community", ega_result$wc["mean_loss"], "\n")

# What else is in that community?
comm <- ega_result$wc["mean_loss"]
members <- names(ega_result$wc)[ega_result$wc == comm]
cat("\nCommunity", comm, "(containing Loss):\n")
cat("  Members:", paste(short_labels[members], collapse = ", "), "\n")
```

```{r}
#| label: boot-ega
#| fig-cap: "Bootstrap EGA — stability of community assignments"

set.seed(42)
boot_ega <- bootEGA(df_win, iter = 500,
                    model = "glasso",
                    algorithm = "walktrap",
                    type = "parametric",
                    verbose = FALSE)

cat("Modal number of communities across bootstraps:",
    as.numeric(names(sort(table(boot_ega$n.dim), decreasing = TRUE))[1]), "\n")

# Structural consistency
cat("\nItem stability (proportion of bootstraps in modal community):\n")
stab <- boot_ega$frequency
print(round(stab, 3))
```


# Section 7 — Network Stability (bootnet)

```{r}
#| label: boot-edges
#| fig-cap: "Bootstrap confidence intervals for edge weights"
#| fig-width: 12
#| fig-height: 10

set.seed(42)
boot_nonparam <- bootnet(network, nBoots = 1000, type = "nonparametric",
                         nCores = parallel::detectCores() - 1,
                         verbose = FALSE)

plot(boot_nonparam, labels = net_labels,
     order = "sample", CIstyle = "quantiles")
```

```{r}
#| label: save-edge-boot
#| include: false

pdf("../../fig/network_edge_bootstrap.pdf", width = 12, height = 10)
plot(boot_nonparam, labels = net_labels,
     order = "sample", CIstyle = "quantiles")
dev.off()
cat("Saved to fig/network_edge_bootstrap.pdf\n")
```

```{r}
#| label: boot-centrality
#| fig-cap: "Case-dropping bootstrap for centrality stability"
#| fig-width: 10
#| fig-height: 8

set.seed(42)
boot_case <- bootnet(network, nBoots = 1000, type = "case",
                     statistics = c("strength", "expectedInfluence",
                                    "betweenness", "closeness"),
                     nCores = parallel::detectCores() - 1,
                     verbose = FALSE)

plot(boot_case, statistics = c("strength", "expectedInfluence",
                                "betweenness", "closeness"))
```

```{r}
#| label: cs-coefficients

cs_coefs <- corStability(boot_case)
cat("CS-coefficients (correlation stability):\n")
print(cs_coefs)

cat("\nInterpretation guidelines:\n")
cat("  CS >= 0.50: Good, centrality is stable and interpretable\n")
cat("  CS >= 0.25: Acceptable minimum\n")
cat("  CS < 0.25: Centrality should NOT be interpreted\n")
```


# Section 8 — Bridge Centrality

```{r}
#| label: bridge-centrality
#| fig-cap: "Bridge centrality using EGA-derived communities"
#| fig-width: 10
#| fig-height: 8

# Use EGA communities for bridge analysis
ega_communities <- ega_result$wc

bridge_result <- bridge(network$graph, communities = ega_communities)

# Manual plot — plot.bridge() is broken with newer ggplot2 (aes_string deprecated)
bridge_plot_df <- data.frame(
  Variable = rep(short_labels[names(bridge_result$`Bridge Strength`)], 2),
  Measure = rep(c("Bridge Strength", "Bridge Expected Influence (1-step)"), each = length(bridge_result$`Bridge Strength`)),
  Value = c(bridge_result$`Bridge Strength`, bridge_result$`Bridge Expected Influence (1-step)`)
)

bridge_plot_df %>%
  mutate(Variable = reorder(Variable, Value)) %>%
  ggplot(aes(x = Value, y = Variable)) +
  geom_point(size = 3) +
  geom_segment(aes(xend = 0, yend = Variable)) +
  facet_wrap(~ Measure, scales = "free_x") +
  theme_minimal(base_size = 12) +
  labs(x = NULL, y = NULL)
```

```{r}
#| label: bridge-table
#| tbl-cap: "Bridge centrality values"

bridge_df <- data.frame(
  Variable = short_labels[names(bridge_result$`Bridge Strength`)],
  Bridge_Strength = round(bridge_result$`Bridge Strength`, 3),
  Bridge_EI = round(bridge_result$`Bridge Expected Influence (1-step)`, 3),
  Community = ega_communities[names(bridge_result$`Bridge Strength`)]
) %>%
  arrange(desc(Bridge_Strength))

print(bridge_df)

cat("\nPredictability bridge centrality:\n")
print(bridge_df %>% filter(Variable == "Loss"))
```


# Section 9 — Network Comparison by Proficiency Level

```{r}
#| label: proficiency-split

# Compute mean overall rater score
df_raw_complete <- df_raw[complete.cases(df_raw[, feature_vars[feature_vars != "clauses_per_tunit"]]), ]
df_raw_complete$Overall_mean <- rowMeans(df_raw_complete[, c("Overall_1", "Overall_2")], na.rm = TRUE)

# Define proficiency groups
df_raw_complete$prof_group <- case_when(
  df_raw_complete$Overall_mean <= 2.5 ~ "Low",
  df_raw_complete$Overall_mean >= 4.0 ~ "High",
  TRUE ~ "Mid"
)

cat("Proficiency group sizes:\n")
print(table(df_raw_complete$prof_group))

# Select feature columns (without clauses_per_tunit)
keep_vars <- setdiff(feature_vars, "clauses_per_tunit")

df_low <- df_raw_complete %>%
  filter(prof_group == "Low") %>%
  select(all_of(keep_vars)) %>%
  mutate(across(everything(), winsorize))

df_high <- df_raw_complete %>%
  filter(prof_group == "High") %>%
  select(all_of(keep_vars)) %>%
  mutate(across(everything(), winsorize))

cat("\nLow proficiency n:", nrow(df_low), "\n")
cat("High proficiency n:", nrow(df_high), "\n")
```

```{r}
#| label: estimate-group-networks

net_low <- estimateNetwork(df_low, default = "EBICglasso", tuning = 0.5)
net_high <- estimateNetwork(df_high, default = "EBICglasso", tuning = 0.5)
```

```{r}
#| label: group-network-plots
#| fig-cap: "Network comparison: Low vs High proficiency"
#| fig-width: 14
#| fig-height: 7

# Use the same layout for both (average of spring layouts)
avg_layout <- averageLayout(net_low$graph, net_high$graph)

par(mfrow = c(1, 2))

qgraph(net_low$graph,
       layout = avg_layout,
       labels = net_labels,
       groups = groups,
       color = group_colors,
       legend = FALSE,
       borders = TRUE,
       border.width = 1.5,
       vsize = 7,
       esize = 8,
       posCol = "#2166AC",
       negCol = "#B2182B",
       title = "Low Proficiency",
       title.cex = 1.3,
       maximum = max(abs(c(net_low$graph, net_high$graph))))

qgraph(net_high$graph,
       layout = avg_layout,
       labels = net_labels,
       groups = groups,
       color = group_colors,
       legend = FALSE,
       borders = TRUE,
       border.width = 1.5,
       vsize = 7,
       esize = 8,
       posCol = "#2166AC",
       negCol = "#B2182B",
       title = "High Proficiency",
       title.cex = 1.3,
       maximum = max(abs(c(net_low$graph, net_high$graph))))

par(mfrow = c(1, 1))
```

```{r}
#| label: save-group-plots
#| include: false

pdf("../../fig/network_group_comparison.pdf", width = 14, height = 7)
par(mfrow = c(1, 2))
qgraph(net_low$graph,
       layout = avg_layout, labels = net_labels,
       groups = groups, color = group_colors, legend = FALSE,
       borders = TRUE, border.width = 1.5, vsize = 7, esize = 8,
       posCol = "#2166AC", negCol = "#B2182B",
       title = "Low Proficiency", title.cex = 1.3,
       maximum = max(abs(c(net_low$graph, net_high$graph))))
qgraph(net_high$graph,
       layout = avg_layout, labels = net_labels,
       groups = groups, color = group_colors, legend = FALSE,
       borders = TRUE, border.width = 1.5, vsize = 7, esize = 8,
       posCol = "#2166AC", negCol = "#B2182B",
       title = "High Proficiency", title.cex = 1.3,
       maximum = max(abs(c(net_low$graph, net_high$graph))))
par(mfrow = c(1, 1))
dev.off()
cat("Saved to fig/network_group_comparison.pdf\n")
```

```{r}
#| label: nct
#| fig-cap: "Network Comparison Test results"
#| output: false

set.seed(42)
nct_result <- NetworkComparisonTest::NCT(
  net_low, net_high,
  it = 1000,
  test.edges = TRUE,
  test.centrality = TRUE,
  centrality = c("strength", "expectedInfluence"),
  verbose = FALSE
)

cat("=== Network Comparison Test Results ===\n\n")

cat("1. Omnibus test (network structure invariance):\n")
cat("   M statistic:", round(nct_result$nwinv.real, 4), "\n")
cat("   p-value:", round(nct_result$nwinv.pval, 4), "\n\n")

cat("2. Global strength invariance:\n")
cat("   Strength difference:", round(nct_result$glstrinv.real, 4), "\n")
cat("   p-value:", round(nct_result$glstrinv.pval, 4), "\n\n")

cat("3. Significant individual edge differences (p < 0.05):\n")
sig_edges <- nct_result$einv.pvals %>%
  filter(`p-value` < 0.05)

if (nrow(sig_edges) > 0) {
  print(sig_edges)
} else {
  cat("   No individual edges significantly differ between groups.\n")
}
```

```{r}
#| label: nct-predictability

# Focus on predictability-related edge differences
cat("Edge weight differences involving predictability nodes:\n\n")

adj_low <- net_low$graph
adj_high <- net_high$graph

pred_comparison <- data.frame(
  Partner = short_labels[colnames(adj_low)],
  Low_Loss = round(adj_low["mean_loss", ], 3),
  High_Loss = round(adj_high["mean_loss", ], 3),
  Diff_Loss = round(adj_high["mean_loss", ] - adj_low["mean_loss", ], 3)
) %>%
  filter(Partner != "Loss") %>%
  arrange(desc(abs(Diff_Loss)))

print(pred_comparison)
```


# Summary & Interpretation

```{r}
#| label: summary

cat("=" %>% strrep(60), "\n")
cat("SUMMARY OF NETWORK ANALYSIS RESULTS\n")
cat("=" %>% strrep(60), "\n\n")

# 1. Community structure
cat("1. COMMUNITY STRUCTURE (EGA)\n")
cat("   Number of communities:", ega_result$n.dim, "\n")
cat("   mean_loss assigned to community:", ega_result$wc["mean_loss"], "\n\n")

# What's in the same community as predictability?
pred_comm <- ega_result$wc["mean_loss"]
same_comm <- names(ega_result$wc)[ega_result$wc == pred_comm]
cat("   Variables in same community as predictability:\n")
cat("  ", paste(short_labels[same_comm], collapse = ", "), "\n\n")

# 2. Centrality
cat("2. CENTRALITY\n")
cent_sorted <- cent %>% arrange(desc(Strength))
cat("   Top 3 by strength:", paste(cent_sorted$Variable[1:3], collapse = ", "), "\n")
loss_rank <- which(cent_sorted$Variable == "Loss")
cat("   mean_loss strength rank:", loss_rank, "of", nrow(cent_sorted), "\n\n")

# 3. Bridge centrality
cat("3. BRIDGE CENTRALITY\n")
cat("   (See bridge table above for predictability bridge scores)\n\n")

# 4. Interpretation framework
cat("4. INTERPRETATION RELATIVE TO CFA HYPOTHESES\n")
cat("   | CFA Model | Supporting Evidence |\n")
cat("   |-----------|--------------------|\n")
cat("   | Model 1 (Phraseological) | Predictability in same community as MI? ",
    pred_comm == ega_result$wc["amod_mi"], "|\n")
cat("   | Model 2 (General factor)  | High centrality? Loss rank =", loss_rank, "|\n")
cat("   | Novel finding             | Check community membership above |\n\n")

# 5. Stability
cat("5. STABILITY\n")
cat("   CS-coefficients reported in Section 7\n")
cat("   Edge accuracy CIs reported in Section 7\n\n")

# 6. Proficiency differences
cat("6. PROFICIENCY GROUP DIFFERENCES\n")
cat("   Network structure invariance p =", round(nct_result$nwinv.pval, 4), "\n")
cat("   Global strength invariance p =", round(nct_result$glstrinv.pval, 4), "\n")
```
